---
title: "Filter observations"
output:
learnr::tutorial:
progressive: true
allow_skip: true
runtime: shiny_prerendered


---
  
  ```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(nycflights13)
library(Lahman)


tutorial_options(
  exercise.timelimit = 60,
  # A checker function that compares the expected and actual results
  exercise.checker = function(label, user_code, solution_code, check_code, envir_result, evaluate_result, ...) {
    user_result <- eval(parse(text = user_code), envir = envir_result)
    correct_result <- eval(parse(text = solution_code), envir = envir_result)
    if (nrow(user_result) == nrow(correct_result) && all.equal(user_result, correct_result) == TRUE) {
      return(list(correct = TRUE, message = "Great job!"))
    } else {
      return(list(correct = FALSE, message = "Check your filtering conditions and try again."))
    }
  }
)


knitr::opts_chunk$set(error = TRUE)
  ```
## Welcome

This is a chopped up tutorial I stole from [github](https://github.com/rstudio/learnr/blob/main/inst/tutorials/ex-data-filter/ex-data-filter.Rmd). We can do all kinds of fun Rmd in here and then do questions with hints and right / wrong like I show below. Yay for interns learning. 

the correct answer to the question is something equivalent to this: filter(flights, dep_delay > 60, (dep_delay - arr_delay) > 30)


### Common mistakes
Me (Derek) thinking I can code in R


## Exercises

### Exercise 1


1. Were delayed more than an hour, but made up more than 30 minutes in flight ## minimal viable sample makes this entirely out of context, the important thing is the checker is working and we can easily copy this format to make all the questions we could ever want. Possibly we make it Happiness Survey Related?

    ```{r filterex1, exercise = TRUE}

    ```
    ```{r filterex1-solution}
    filter(flights, dep_delay > 60, (dep_delay - arr_delay) > 30)
    ```

    <div id="filterex1-hint">
    **Hint:** The time a plane makes up is `dep_delay - arr_delay`.
    </div>
    
  ```{r filterex1-check}
   "idk why there needs to be text in here"
  ```
